
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "C:/Users/Admin/Desktop/World_Bank")
```
---
title: "WBData"
author: "Samiratou Kora Chabi"
date: "03/03/2022"
output:
  html_document: default


editor_options: 
  chunk_output_type: inline
---
---
knit: (function(Code_R, UTF-8) {
  out_dir <- "docs";
  rmarkdown::render(Code_R,
 encoding="UTF-8",
 output_file=Code,output_dir= "C:/Users/Admin/Desktop/essay/WB")})
 
---


```{r}
getwd()
```

# Check installed packages

```{r}
installed.packages(c("styler","lintr","WDI","ggplot2","rmarkdown","reshape2","dplyr","tidyr","knit"))
```
# Load packages

```{r}
library(knitr)
library(rmarkdown)
library(styler)
library(lintr)
library(WDI)
library(ggplot2)
library(reshape2)
library(dplyr)
library(tidyr)
 
```

# Dowload series  for some countries using world bank gender data portal

## Load data about account ownership in some countries of west africa

**Definition of variable**

*FX.OWN.TOTL.FE.ZS: Account ownership at a financial institution or with a mobile-money-service provider, female (% of population ages 15+)

```{r}
dat = WDI(indicator='FX.OWN.TOTL.FE.ZS', country=c('CMR','BFA','BEN'), start=2010, end=2020)
```
```{r}
dat1 = WDI(indicator='FX.OWN.TOTL.FE.ZS', country=c('CMR','BEN','SEN'), start=2010, end=2020)
```

## Load data about employment in industry, agriculture and services in some countries of west africa

**List of variables** 

*SL.EMP.MPYR.FE.ZS: Employers, female (% of female employment)

*SL.EMP.MPYR.MA.ZS: Employers, male (% of male employment) 	

*SL.EMP.MPYR.ZS: Employers, total (% of total employment) 

*SL.AGR.EMPL.ZS: Employment in agriculture (% of total employment) 

*SL.AGR.EMPL.FE.ZS: Employment in agriculture, female (% of female employment) 	

*SL.AGR.EMPL.MA.ZS: Employment in agriculture, male (% of male employment) 

*SL.IND.EMPL.ZS: Employment in industry (% of total employment) 

*SL.IND.EMPL.FE.ZS: Employment in industry, female (% of female employment) 

*SL.IND.EMPL.MA.ZS: Employment in industry, male (% of male employment) 

*SL.SRV.EMPL.ZS: Employment in services (% of total employment) 

*SL.SRV.EMPL.FE.ZS: Employment in services, female (% of female employment) 

*SL.SRV.EMPL.MA.ZS: Employment in services, male (% of male employment) 

```{r}
dat2=WDI(indicator=c('SL.EMP.MPYR.FE.ZS','SL.EMP.MPYR.MA.ZS','SL.EMP.MPYR.ZS','SL.AGR.EMPL.ZS','SL.AGR.EMPL.FE.ZS','SL.AGR.EMPL.MA.ZS','SL.IND.EMPL.ZS','SL.IND.EMPL.FE.ZS','SL.IND.EMPL.MA.ZS','SL.SRV.EMPL.ZS','SL.SRV.EMPL.FE.ZS','SL.SRV.EMPL.MA.ZS'),country=c('CAN','MEX','FRA','USA'),start=2010, end=2019)

dat2=WDI(indicator=c('SL.EMP.MPYR.FE.ZS
'),country=c('CAN','MEX','FRA','USA'),start=2010, end=2019)

```

# Look at the data
```{r}
head(dat)
```
```{r}
head (dat1)
```
```{r}
head (dat2)
```

# Plot the data using dataset dat1

```{r}
dat1 = WDI(indicator='FX.OWN.TOTL.FE.ZS', country=c('CMR','BEN','SEN'), start=2010, end=2020)

ggplot(dat1, aes(year, FX.OWN.TOTL.FE.ZS, color=country, group=country)) + geom_line() + 
  xlab('Year') + ylab('Account ownership') +
  scale_x_continuous(limits=c(2010, 2018), breaks = seq(2010, 2018, 3),
                     expand = c(0, 0)) + geom_point(na.rm = TRUE)+
  ggtitle("Account ownership,  female (% of population ages 15+)
")

```

# Plot the data using dataset dat2

```{r}
dat2=WDI(indicator=c('SL.EMP.MPYR.FE.ZS','SL.EMP.MPYR.MA.ZS','SL.EMP.MPYR.ZS','SL.AGR.EMPL.ZS','SL.AGR.EMPL.FE.ZS','SL.AGR.EMPL.MA.ZS','SL.IND.EMPL.ZS','SL.IND.EMPL.FE.ZS','SL.IND.EMPL.MA.ZS','SL.SRV.EMPL.ZS','SL.SRV.EMPL.FE.ZS','SL.SRV.EMPL.MA.ZS'),country=c('CAN','MEX','FRA','USA'),start=2010, end=2019)

ggplot(data = dat2, aes(x = year, y = SL.EMP.MPYR.FE.ZS, color = country)) +
  geom_line(aes(color= country))+ geom_point(na.rm = TRUE)+
  scale_x_continuous(limits=c(2010, 2019), breaks = seq(2010, 2018, 1),
                     expand = c(0, 0)) +  
  xlab('Year') + ylab('Female employment') +
  ggtitle("Employers, female (% of female employment)")

dat2$id<-1:nrow(dat2)
dat2m10<-pivot_longer(subset(dat2,year==2010), -c(country,year,iso2c,id,'SL.EMP.MPYR.FE.ZS','SL.EMP.MPYR.MA.ZS','SL.EMP.MPYR.ZS'), names_to="variables", values_to="value")

dat2m19<-pivot_longer(subset(dat2,year==2019), -c(country,year,iso2c,id,'SL.EMP.MPYR.FE.ZS','SL.EMP.MPYR.MA.ZS','SL.EMP.MPYR.ZS'), names_to="variables", values_to="value")

ggplot(dat2m10,aes(x = country,y = value)) + 
    geom_bar(aes(fill = variables),stat = "identity",position = "dodge")+ 
  ggtitle("Employment in agriculture, service and industry in 2010 (% of total employment)")

ggplot(dat2m19,aes(x = country,y = value)) + 
    geom_bar(aes(fill = variables),stat = "identity",position = "dodge")+ 
  ggtitle("Employment in agriculture, service and industry in 2019 (% of total employment)")
```




